---
title: "lab 8"
author: "Margaret Hammond"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach Packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

## Read in Data
```{r}
homes <- read_csv(here("slo_homes.csv"))
```

A little bit of cleaning:

Make a subset called homes_sub that only contains observations (rows) where the city is:
- SLO
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt
```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo",
         "Arroyo Grande",
         "Atascadero",
         "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status):

- Find & return in a nice summary table the mean and standard deviation of home price, grouped by city and sales status.

```{r, include = FALSE, eval = FALSE}
homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

# Actually I don't even want to run this code. Then eval = FALSE

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +
  scale_x_continuous(limits = c(0, 3e6))
  
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City and point shape by sale status

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point() +   #aes(color = City, shape = Status)) +
  geom_smooth(method = "lm")
```

