---
title: "lab 8"
author: "Margaret Hammond"
date: "11/15/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach Packages
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

## Read in Data
```{r}
homes <- read_csv(here("slo_homes.csv"))
```

A little bit of cleaning:

Make a subset called homes_sub that only contains observations (rows) where the city is:
- SLO
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt
```{r}
homes_sub <- homes %>% 
  filter(City %in% c("San Luis Obispo",
         "Arroyo Grande",
         "Atascadero",
         "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status):

- Find & return in a nice summary table the mean and standard deviation of home price, grouped by city and sales status.

```{r, include = FALSE, eval = FALSE}
homes_sub %>% 
  group_by(City, Status) %>% 
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

# Actually I don't even want to run this code. Then eval = FALSE

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +
  scale_x_continuous(limits = c(0, 3e6))
  
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City and point shape by sale status

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point() +   #aes(color = City, shape = Status)) +
  geom_smooth(method = "lm")
```

## Model the relationship with home price as DV

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)

# Make a subset that only contains the quantitative variables

homes_quant <- homes_sub %>% 
  select(Price:PricePerSqFt)

homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor, method = 'ellipse')

# How would I explore diagnostic plots?
plot(homes_lm1)
```

homes_lm1 is a crap model. 

Try another model (homes_lm2) where we simplify this a bit:

- City
- SqFt
- Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)

homes_lm2

homes_lm3 <- lm(Price ~ City + SqFt + Status + PricePerSqFt, data = homes_sub)

plot(homes_lm2)

# For homes_lm1, The R squared value is 0.8457. This means that 85% of the variance of the dependent variable is explained by the model. 85% of the variance in price is explained by the predictor variables within the model.

```

Find the AIC value of each model:

```{r}
AIC(homes_lm1)
AIC(homes_lm2)
AIC(homes_lm3)

#Lower AIC value is better fit. 
```

Use `modelsummary` to show model outputs side-by-side:

If you use modelsummary to return model utputs of multiple models, it wants you to feed it to it as a list.
```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

Take away: model selection is hard!!! It takes critical thought

## Start naking predictions with this model

Use `broom::augment()`

```{r}
homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function to try out your model on new scenarios that you create.

```{r}

```

